---
title: "Multiple Selections"
subtitle: "Dealing with multiple selections to speed up adding lines & shapes."
author: "Brady Johnston"
date: '2021-03-02'
output:
  # md_document:
  #   pandoc_args: ["--wrap=preserve"]
  html_document:
    theme: flatly
    highlight: pygments
---

<!--
%\VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{Multiple Selections}
-->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## What is in a selection

Selections in `{r3dmol}` are provided via the `m_sel()` function. These 
selections are then interpreted by by `3Dmol.js` that is the underlying 
molecular library. 

When dealing with styles, `3Dmol.js` works on every atom inside the `m_sel()`. 
When creating new objects such as lines, spheres or cylinders and `3Dmol.js` 
interprets these selections by finding the **middle-most-point** of the 
selection.

If we look at the code below, the styles are being applied to the residue
number 2. Each atom of the selection `m_sel(resi = 2, chain = "A")` has the 
specified styles applied to it.

```{r}
library(r3dmol)

model <- r3dmol() %>%
  m_add_model(pdb_6zsl) %>%
  m_set_style(m_style_stick(hidden = TRUE)) %>%
  m_add_style(
    style = c(
      m_style_stick(),
      m_style_sphere(scale = 0.3)
    ),
    sel = m_sel(resi = 2, chain = "A")
  ) %>%
  m_zoom_to(m_sel(resi = 2, chain = "A"))

model %>%
  m_add_res_labels(m_sel(resi = 2, chain = "A"),
    style = m_style_label(inFront = FALSE)
  ) %>%
  m_spin()
```

What if we add a shape to this scene, using the same selection
`m_sel(resi = 2, chain = "A")`?

```{r}
model %>%
  m_add_sphere(
    center = m_sel(resi = 2, chain = "A"),
    spec = m_shape_spec(
      wireframe = TRUE,
      color = "BLUE"
    )
  ) %>%
  m_spin()
```

We see that only a single sphere was added because only a single 
selection was supplied. `3Dmol.js` found the _middle-point_ of that selection, 
and that is where the sphere was created.

## Multiple selections

Some functions in `{r3dmol}` can take multiple selections as a list, to speed
up the process of creating objects without having to call `m_add_*()` multiple 
times.

### Add more residues

First, let's add a few more residues to our viewer and add labels so we can keep
track of what is going where.

```{r}
model <- model %>%
  m_set_style(
    style = c(
      m_style_stick(),
      m_style_sphere(scale = 0.3)
    ),
    sel = m_sel(resi = c(2, 4, 6, 8), chain = "A")
  ) %>%
  m_zoom_to(m_sel(resi = 2:8, chain = "A")) %>%
  m_spin(speed = 0.5) %>%
  m_add_res_labels(
    m_sel(
      resi = c(2, 4, 6, 8),
      chain = "A"
    ),
    style = m_style_label(inFront = FALSE)
  )

model
```

## Adding lines

Using the `m_add_line()` we can add lines between selections. 

One method is to do a new `m_add_line()` for each line. 

Notice how, just like  `m_add_sphere()`, the middle of the selection for the
`start` and `end` positions were found, and that is where the line was drawn.

```{r}
model %>%
  m_add_line(
    start = m_sel(resi = 2, chain = "A"),
    end = m_sel(resi = 4, chain = "A"),
    color = "green",
    dashed = FALSE
  ) %>%
  m_add_line(
    start = m_sel(resi = 6, chain = "A"),
    end = m_sel(resi = 8, chain = "A"),
    color = "blue"
  )
```

Alternatively, you can supply multiple `start` and `end` selections and multiple
lines will be created. You must provide equal numbers of `start` and `end` 
selections.

You can also supply aesthetic values to the single `m_add_line()` function. 
These can be either of `length == 1`, in which case the aesthetic will be 
applied to all lines (as with the `dashed` argument in the example below) or 
`length == #lines` where the aesthetic vector must have a value for each of the 
lines being created (as in the `color` argument in the example below).

```{r}
model %>%
  m_add_line(
    start = list(
      m_sel(resi = 2, chain = "A"),
      m_sel(resi = 4, chain = "A")
    ),
    end = list(
      m_sel(resi = 6, chain = "A"),
      m_sel(resi = 8, chain = "A")
    ),
    dashed = FALSE,
    color = c("green", "red")
  )
```


## Using `m_muli_resi_sel()`

To make it easier to supply multiple selections, the `m_multi_resi_sel()` 
function returns a list of `m_sel()` selections, which have all of the same
selection criteria, but only contain a single residue each. 

This single function selection:
```{r, eval = FALSE}
m_multi_resi_sel(resi = 2:4, chain = "A")
```

Is the same as the list of `m_sel()` selections.
```{r, eval = FALSE}
list(
  m_sel(resi = 2, chain = "A"),
  m_sel(resi = 3, chain = "A"),
  m_sel(resi = 4, chain = "A")
)
```
We can then use this to supply multiple selections to the `start` and `end` 
arguments of `m_add_line()`.
```{r}
model %>%
  m_add_line(
    start = m_multi_resi_sel(resi = c(2, 4), chain = "A"),
    end = m_multi_resi_sel(resi = c(6, 8), chain = "A"),
    dashed = c(FALSE, TRUE),
    color = "green"
  )
```

This can be applied to as many lines as required by increasing the number
of residues selected with `m_multi_resi_sel()`.

```{r}
model %>%
  m_add_style(m_style_cartoon()) %>%
  m_add_line(
    start = m_multi_resi_sel(resi = 2:51, chain = "A"),
    end = m_multi_resi_sel(resi = 2:51, chain = "B"),
    dashed = rep(c(TRUE, FALSE), 25),
    color = rep(c("blue", "red"), 25)
  ) %>%
  m_zoom_to()
```
