---
title: "Styling Your Protein"
author: "Brady Johnston"
date: '`r Sys.Date()`'
output:
  # md_document:
  #   pandoc_args: ["--wrap=preserve"]
  html_document:
    theme: flatly
---

<!--
%\VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{Style Functions}
-->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<!-- # User-Friendly Approach -->

### Styling in {r3dmol}

To style a model, you can either `m_add_style()` or `m_set_style()`, which 
will either _add_ styling to what is already in the scene, or _overwrite_ the 
styling for the selection in the call. The `m_style_surface()` and 
`m_style_label()` must be used inside `m_add_surface()` and `m_add_label()` 
functions, and cannot be supplied inside the `m_set_style()` or `m_add_style()`.

By default, the _line_ styling is applied when a new model is added to the 
scene. If you don't want the line styling, use `m_set_style()` after adding
a model to the scene.

Some styles have additional, more advanced options that involve javascript, 
details for all of this can be found in the 
[documentation for 3dmol.js](https://3dmol.csb.pitt.edu/).

```{r load-package}
library(r3dmol)
```


```{r}
model <- r3dmol() %>% 
  m_add_model(data = pdb_6zsl) %>% 
  m_set_style(style = m_style_cartoon()) %>% 
  m_zoom_to()

model
```

## Style Options

All of the styling functions have multiple options. These vary, depending on the
style chosen but are all described in the function documentation.

```{r}
model %>% 
  m_set_style(style = m_style_cartoon(color = 'spectrum', ribbon = TRUE)) %>% 
  m_add_outline() %>% 
  m_set_zoom_limits(upper = 200, lower = 30)

```


Multiple styles can be supplied by placing multiple styles inside `c()` into the 
`style` parameter.

```{r}
model %>%
  m_set_style(style = c(
    m_style_cartoon(
      color = "spectrum",
      ribbon = TRUE
    ),
    m_style_line()
  ))
```

## Using Selections

In order to selectively apply styling to a model, usage of the `m_sel()` 
function allows specification of particular atoms to apply the style to.

The `m_sel()` is a generic selection function, and can be used anywhere that a 
selection is required. Selections can be specified with:
* `resn` = Residue Name
* `resi` = Residue Number
* `chain` = Chain letter
* `model` = Model index in the scene

To name a few of the useful selection options. Check the documentation
for more available options. 

```{r}
model %>%
  m_add_style(
    style = c(
      m_style_stick(),
      m_style_sphere(scale = 0.3)
    ),
    sel = m_sel(resi = 1:10, chain = "A")
  ) %>%
  m_zoom_to(sel = m_sel(resi = 1:10, chain = "A"))
```

Selections can be supplied for functions that require a single point. The center
of the overall selection will be found, and that value used in the function.

In the example below, when adding the _start_ and _end_ points for the line, 
the chain is specified (but the middle-point of all 10 residues is found and 
used) but when adding the label, the chain specification is left out.

The middle of residues 1-10 from both chains is found, and that is where the 
label is placed.

```{r}
model %>%
  m_add_style(
    sel = m_sel(resi = 1:10),
    style = c(
      m_style_stick(),
      m_style_sphere(scale = 0.3)
    )
  ) %>%
  m_add_line(
    start = m_sel(
      resi = 1:10,
      chain = "A"
    ),
    end = m_sel(
      resi = 1:10,
      chain = "B"
    ), spec = list(dashed = TRUE)
  ) %>%
  m_add_label(
    text = "The middle of the selection",
    sel = m_sel(resi = 1:10)
  )
```



## Loading Functions

Models can be fetched from the PDB database using `m_fetch_pdb()`.

Models from the common structural analysis and bioinformatics package {bio3d} 
can be add with the `m_bio3d()` function.

```{r, eval=TRUE}
model <- r3dmol() %>% 
  m_add_model(data = m_fetch_pdb("1bna", save.pdb = FALSE)) %>% 
  m_set_style(style = m_style_cartoon()) %>% 
  m_zoom_to()
model
```

Obtaining package through `bio3d`, then reading into `r3dmol`.

```{r}
library(bio3d)
pdb <- read.pdb("1bna") 

pdb

model2 <- r3dmol() %>% 
  m_add_model(data = m_bio3d(pdb)) %>% 
  m_set_style(style = m_style_cartoon()) %>% 
  m_zoom_to()

model2
```



